Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Reintroduce deleted absolute value
Fix terminology

  \todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for a set of $N$-dimensional
  points $P$ is written as $|P|$ and is defined:
%
  \begin{align*}
    |P| & = \sum_{i=1}^{N} dist_i(P)
    &
    \textit{dist}_i(P) & = \begin{cases}
      0 & \pi_i(P) = \interv{-\infty}{\infty}{} \\
      \mathsf{a} - 1 & \pi_i(P) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?
  }
\end{proof}

\todo{%
  We used to call the below property contiguity, and I think this is a natural
  notion- does ``close neighbour'' have some standard use or is it okay to call
  this contiguity?
}
\begin{defn}{(Close neighbour)}
  A set of points $P$ is said to be a \emph{close neighbour at index $j$} of a
  set $P'$ if for every index $i$ except $j$, $\pi_i(P) = \pi_i(P')$ but at $j$
  then $\pi_j(P) \neq \pi_i(P')$ and $\textit{dist}_j(P) = \textit{dist}_i(P') +
  1$.

@@

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$-dimensional set of
  points, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}

>>>>

  \todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $|S|$ and is defined as:
%
  \begin{align*}
    |S| & = \sum_{i=1}^{N} dist_i(S)
    &
    \textit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?

    Response: The definition says extended origin distance is the smallest
    number of translations to reach the extended origin, we need to prove that
    this formula indeed gives that.
  }
\end{proof}

\todo{%
  We used to call the below property contiguity, and I think this is a natural
  notion- does ``close neighbour'' have some standard use or is it okay to call
  this contiguity?

  Response: how about adjecency?
}
\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_i(S')$ such that $|S| = |S'| + 1$.

@@

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique adjacent at index $i$ of a subscript, if it exists, is given by the
  following partial function:
%
  \begin{align*}
    \mathit{adjacent}(S,i) & = \prod^{N}_{j=1} \mathit{shift}(S,i,j) &
%
    \mathit{shift}(S,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(S)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}
